---
title: "Homework 1"
author: "Melike Aksoy"
date: 2023-09-23
output: github_document
---

```{r}
library(tidyverse)
```

## 'Problem 1'
Dowloading the package containing the penguins dataset on the console and loading moderndive library

```{r}
library(moderndive)
```

Loading 'early_january_weather' dataset

```{r}
data("early_january_weather")
```

Look at data

```{r}
early_january_weather
```


Look at the data summary

```{r}
str(early_january_weather)

skimr:: skim(early_january_weather)
```

Mean 'temperature'

```{r}

```

## Discussion: early_january_weather data includes 15 variables (origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour). There are 1 character variable (origin) and 13 numeric variable (year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib) and 1 posixct variable (time_hour) present in the data. There are 358 rows and 15 columns present in this dataset. The mean temp 


