---
title: "Homework 1"
author: "Melike Aksoy"
date: 2023-09-23
output: github_document
---

# `Problem 1`

#### Dowloading the package containing the penguins dataset on the console and loading library for moderndive , ggplot, and tidyverse

```{r, message=FALSE}
library(tidyverse)
library(moderndive)
library(ggplot2)
```


#### Loading 'early_january_weather' dataset

```{r, eval=FALSE}
data("early_january_weather")
```

#### Look at data

```{r, eval=FALSE}
#early_january_weather
```


#### Look at the data summary

```{r, eval=FALSE}
str(early_january_weather)

skimr:: skim(early_january_weather)
```


#### Checking the variable names in the dataset
```{r, eval=FALSE}
help("early_january_weather")
```

## Description of the dataset:

The dataset includes the hourly meterological data for LGA, JFK, EWR for the month of January 2013. The data includes variables origin(weather station), year(time of recording), month(time of recording), day(time of recording), hour(time of recording), temp(temperature in F), dewp(dewpoint in F), humid(Relative humidity), wind_dir(wind direction(in direction)), wind_speed(wind speed), wind_gust(gust speed (in mph)), precip(Precipitation, in inches), pressure(sea level pressure in millibars), visib (visibility in miles), and time_hour(date and hour of the recording). The values of the important variables are `r round (mean(early_january_weather$visib))` for mean values of visibility and `r round (mean(early_january_weather$dewp))` for mean values for dew point. There are `r nrow(early_january_weather)` observations(rows) and `r ncol(early_january_weather)` variables(columns) present in this dataset. The mean temperature in F is `r round (mean(early_january_weather$temp))`.


#### Making a scatterplot and exporting to my project directory

```{r, message=FALSE}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

## Description of the Scatterplot:

The scatterplot shows that as time_hour(date and hour of the recording) increases, temperature increases as well. This means that as from the beginning of the January 2013 to the middle of January 2013, temperatures increased. The relationship between time_hour and temperature appears to be a positive linear relationship. Also, humidity tends to increase with time and temperatures. 


# `Problem 2`

#### Creating the data frame comprised of:

1) a random sample of size 10 from a standard Normal distribution
2) a logical vector indicating whether elements of the sample are greater than 0
3) a character vector of length 10
4) a factor vector of length 10, with 3 different factor “levels”

```{r, message=FALSE}
problem2_df=
  tibble(
    samp=rnorm(10,0,1),
    vec_char=c("cancer", "stroke", "asthma", "epilepsy","dementia",   "diabetes", "anxiety", "depression", "hypertension", "eczema"),
    vec_logical=samp>0,
    vec_factor=as.factor(c("High", "Low", "Medium", "Low","High",     "Medium", "High", "High", "Medium", "Low"))
  )
```

